Where and Why Does the Model Failed? A Visual Analytics Tool for Debugging and Interpreting Text Entailment Model

### 2018-02-22 paper/intro.tex
update intro

% (What is the high level motivation)
% What is the obsatcle for effectively apply machine learning model
With the recent advances in neural network based model, machine learning has
gained unprecedented popularity and its adaption permeated many fields of studies.
%
However, from researchers to practitioners, one often need to overcome many obstacles during the training, debugging, tuning process in order to unleash the full potential of these powerful models.
%
Identify where and how does the error occur and understand why does the model fail is critical to the design and application of various models.
%quickly identify where the errors are
However, providing meaningful answers to these questions is an extremely challenging task.
% Naturally the identification of failure scenarios is an important first step in diagnosing procedure.
%the potential limitation of the test dataset
On one hand, the standard evaluation approach provide limited information. Often only performance number is used (i.e., prediction accuracy on the test set) without answering many important questions for the diagnostic process. It would be extremely useful to understand what are the often made mistakes, and how sensitive are the model with respect to perturbation in the input, etc. On the other hand, the understanding why the model fail is even more challenging, which likely require the ability to peak into the model and make sense of the key mechanisms.

Making sense and explaining predictions made by neural networks is also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
%
Due to these demands, many works has been dedicated to providing an more intuitive explanation for a given prediction. Such a system often approach the problem from a model agnostic approach that made them applicable to different applications (i.e. by fitting a similar linear model near the sample of interests).
%
However, these methods despite being invaluable for the prediction interpablity task, do not adequently address the challenge in the model diagnostic process. More importantly, due to the model agnotic nature, they often the lack of the ability to access and explore the inner states of the model, which is vitally important to make sense of why a model fail.

In this work, we introduce a visualization system that through a tight yet flexible integration between visualization and the underlying model, allow user to interrogate the model by perturbing the input, the internal state, as well as prediction output, while observing chances in other part of the pipeline.
We use textual entailment task~\cite{} as an example to illustrate how this system can help natural language processing (NLP) researchers quickly identify the potential limitation of a NLP models and also probe the inner states of model for interpreting key mechanism such as attention.

>>>>

% (What is the high level motivation)
% What is the obsatcle for effectively apply machine learning model
With the recent advances in neural network based model, machine learning has
gained unprecedented popularity, and its adaption permeated many fields of studies.
%
However, from researchers to practitioners, one often need to overcome many
obstacles during the training, debugging, and tuning processes to unleash
the full potential of these models.
%
Identify where and how does the error occur and understand why does the model
fail is critical to the design and application of various models.
%quickly identify where the errors are
However, providing meaningful answers to these questions is an extremely challenging task.
% Naturally the identification of failure scenarios is an essential first step in diagnosing procedure.
%the potential limitation of the test dataset
On the one hand, the standard evaluation approach provides limited information. Often only performance number is used (i.e., prediction accuracy on the test set) without answering many important questions for the diagnostic process. It would be instrumental to understand what are the often made mistakes, and how sensitive are the model concerning perturbation in the input, etc. On the other hand, the understanding why the model fails is even more challenging, which likely require the ability to peak into the model and make sense of the key mechanisms.

Making sense and explaining predictions made by neural networks is also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
%
Due to these demands, many works have been dedicated to providing a more intuitive explanation for a given prediction. Such a system often approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a similar linear model near the sample of interests).
%
However, these methods despite being invaluable for the prediction interpretation task cannot adequately address the challenge in the model diagnostic process. More importantly, due to the model agnostic nature, they often the lack of the ability to access and explore the inner states of the model, which is vitally important to make sense of why a model fail.

In this work, we introduce a visualization system that through a tight yet flexible integration between visualization and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
We use textual entailment task~\cite{} as an example to illustrate how this system can help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model and also probe the inner states of the model for interpreting key mechanism such as attention.

### 2018-02-22 paper/relatedWorks.tex
update intro

\begin{itemize}
    \item Depth learning vis
    \item Vis
\end{itemize}

How to interpret classification task
\begin{itemize}
    \item What feature / dimension / part-of-the-input should change to
    alter the outcome
    \item What Examples can you provide that is similar to the current
    instance

\end{itemize}

@@

Papers:
\begin{itemize}
    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
    Use partial dependency (varying along one feature and observer how prediction changes)
    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)

\end{itemize}

>>>>

How to interpret classification task
\begin{itemize}
    \item What feature / dimension / part-of-the-input should change to
    alter the outcome
    \item What Examples can you provide that is similar to the current
    instance
\end{itemize}
\begin{itemize}
    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
    Use partial dependency (varying along one feature and observer how prediction changes)
    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)
\end{itemize}

@@

Depth learning vis
\begin{itemize}
    \item ActiVis: Visual Exploration of Industry-Scale Deep Neural Network Models
    \item Analyzing the Training Processes of Deep Generative Models
    \item Visual Diagnosis of Tree Boosting Methods
    \item TreePOD: Sensitivity-Aware Selection of Pareto-Optimal Decision Trees
    \item LSTMVis: A Tool for Visual Analysis of Hidden State Dynamics in Recurrent Neural Networks
    \item Do Convolutional Neural Networks learn Class Hierarchy?
    \item DeepEyes: Progressive Visual Analytics for Designing Deep Neural Networks
\end{itemize}

Less emphasis on where does the fail
